install.packages("bslib")
install.packages("tidyverse")
install.packages("knitr")
---
title: "ANA 515 Assignment 1"
author: Hao Li
date: 2022-6-5
output: 
  html_document:
    theme:bootswatch: *Legacy custom theming*
---

### set up 

```{r setup, include = FALSE}
library(bslib)
library(tidyverse)
library(knitr)
```

### input dataset from url

```{r, include=FALSE}
url <- "https://raw.githubusercontent.com/fivethirtyeight/guns-data/master/full_data.csv"
gun_deaths <- read_csv(url)
```

### get gun death subset

```{r, include=FALSE}
youth <- gun_deaths %>% 
  filter(age <= 65)
```

### summary of youth 
```{r, include=FALSE}
summary(youth)
```

### rows in gun_deaths and youth
```{r, include=FALSE}
n_1 <-nrow(gun_deaths)
n_2 <-nrow(youth)
```

```{r, echo = FALSE}
#This next chunk is inline code.
```

We have data about `r n_1` individuals killed by guns. Only `r n_1-n_2` are older than 65. The distribution of the remainder is shown below: 

### graph the distribution by age
```{r youth-dist, echo = FALSE}
youth %>%
  ggplot(aes(age))+geom_freqpoly(binwidth=1)
```

### graph the distribution by race
```{r race-dist, echo = FALSE}
youth %>%
  ggplot(aes(fct_infreq(race)%>%fct_rev()))+geom_bar()+
  coord_flip()+labs(x="Victim race")
```

